A method for defining dispersed community territories

### 2024-06-14 manuscript/manuscript.qmd
include zenodo doi and citation

All analyses, including the cost-distance modeling and our implementation of the
algorithm, are conducted in the R programming language and environment
[@rcoreteam2023]. For more details, please see Supplementary Materials, which
include all code necessary to reproduce these analyses and the figures in the
text.

>>>>

All analyses, including the cost-distance modeling and our implementation of the
algorithm, are conducted in the R programming language and environment
[@rcoreteam2023]. For more details, please see the Zenodo repository
[@kenneth_blake_vernon_2024_11661270], which includes all code necessary to
reproduce all analyses and figures in the text.
